### 2024-06-18 index.qmd
20240618 - coffee

  - [open an issue](https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook/issues) or [create a pull request](https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook/pulls) on the [book's GitHub repository](https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook).\index{GitHub}
  - [buy me a coffee](https://www.paypal.com/donate/?business=Q4FMMAMFQYTX8&no_recurring=0&item_name=Support+me+in+developing+this+resource+for+fantasy+football+analytics...+Even+a+cup+of+coffee+%28%244.99%29+helps+me+stay+awake%21&currency_code=USD)—Support me in developing this resource for fantasy football analytics... Even a cup of coffee ($4.99) helps me stay awake!

```{=html}
<a href="https://www.buymeacoffee.com/isaactpetersen" target="_blank"><img src="https://cdn.buymeacoffee.com/buttons/v2/default-yellow.png" alt="Buy Me A Coffee" style="height: 60px !important;width: 217px !important;" ></a>

@@

<br>
```

>>>>

  - [open an issue](https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook/issues) or [create a pull request](https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook/pulls) on the [book's GitHub repository](https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook).\index{GitHub}
  - [buy me a coffee](https://www.buymeacoffee.com/isaactpetersen)—Support me in developing this resource for fantasy football analytics... Even a cup of coffee ($4.99) helps me stay awake!

```{=html}
<script type="text/javascript" src="https://cdnjs.buymeacoffee.com/1.0.0/button.prod.min.js" data-name="bmc-button" data-slug="isaactpetersen" data-color="#FFDD00" data-emoji=""  data-font="Lato" data-text="Buy me a coffee" data-outline-color="#000000" data-font-color="#000000" data-coffee-color="#ffffff" ></script>

@@

<br>
<br>
```
